How Do Like and Dislike Buttons Affect Communication?

### 2020-04-07 analyses/analyses.Rmd
- major updates on theory, analyses, and osm

---
title: "How Do Like and Dislike Buttons Affect Communication? A Privacy Calculus Approach to Understanding Self-Disclosure Online in a One-Week Field Experiment"
shorttitle : "Online Supplementary Material: Analyses"
output: 
  html_document:
    self_contained: yes
    mode: selfcontained
    toc: TRUE
    toc_float:
      collapsed: FALSE
    toc_depth: 2
---

@@

```{r r-setup, include=F}
# define packages
packages <- c("cowplot", "devtools", "GGally", "knitr", "lavaan", "magrittr", 
              "MVN", "psych", "pwr", "quanteda", "semTools", "tidyverse")

# install packages
# devtools::install_github("tdienlin/td@v.0.0.2.3")
# lapply(packages, install.packages, character.only = T, quietly = TRUE)

@@

```{r Data-Wrangling, include=F}
# load data
d_raw <- read_csv("data/data_raw.csv")

@@

    # recode
    edu = recode(edu_fac, 
                 "Hauptschulabschluss/Volksschulabschluss" = 1, 
                 "Noch Schüler" = 1,
                 "Realschulabschluss (Mittlere Reife)" = 1,
                 "Abschluss Polytechnische Oberschule 10. Klasse (vor 1965: 8. Klasse)" = 1,
                 "Anderer Schulabschluss:" = 1,
                 "Fachhochschulreife (Abschluss einer Fachoberschule)" = 2,
                 "Abitur, allgemeine oder fachgebundene Hochschulreife (Gymnasium bzw. EOS)" = 2,
                 "Hochschulabschluss" = 3),
    PC01_03 = 8 - PC01_03, 
    SE01_05 = 8 - SE01_05, 
    SE01_06 = 8 - SE01_06,
    PL01 = recode(PL01, "2" = 1, .default = 0),
    PL02 = recode(PL02, "3" = 1, .default = 0),
    PL03 = recode(PL03, "4" = 1, .default = 0),
    PL04 = recode(PL04, "2" = 1, .default = 0),
    IF01_01 = recode(IF01_01, "1" = 1, .default = 0),
    IF01_02 = recode(IF01_02, "1" = 1, .default = 0),

@@

```{r defaults, include=F}
# variable labels
var_names <- c("Privacy concerns", 
               "General gratifications", 
               "Specific gratifications",
               "Privacy deliberation", 
               "Self-efficacy", 
               "General trust", 
               "Specific trust",
               "Self-disclosure")

@@

```{r sample-descriptives, include=F}
# sample descriptives t1
n_t1 <- nrow(d)
age_t1_m <- mean(d$age)
male_t1_m <- mean(d$male, na.rm = TRUE)
college_t1_m <- table(d$edu)[3] / n_t1

# characteristics of posts
n_comments <- sum(d$post_count, na.rm = TRUE)
n_words <- sum(d$words_sum, na.rm = TRUE)
n_time <- sum(d$time_read_MIN, na.rm = TRUE)
n_posts <- sum(d$post_count, na.rm = TRUE)

# speeding
time_crit <- 3 # minimum time on survey
n_speeding <- nrow(filter(d, time_sum_min_t2 < time_crit))

# filter data
d <- filter(d, time_sum_min_t2 > time_crit) # Deletion of fast respondents
d <- filter(d, !is.na(username) & !is.na(id_survey_t2))  # Use only completes

# sample descriptives final data set
n_final <- nrow(d)
age_final_m <- mean(d$age)
male_final_m <- mean(d$male, na.rm = TRUE)
college_final_m <- table(d$edu)[3] / n_final
```

# Measures
## Privacy Concerns
### Items

@@

```{r}
name <- "pricon"
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_03 + PC01_04 + PC01_05 + PC01_06 + PC01_07
"
fit <- sem(model = model, data = d, estimator = "MLM")
```

#### Model fit

@@

#### Factor loadingss

@@

### CFA updated

```{r}
name <- "pricon"
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
"
fit <- sem(model = model, data = d, estimator = "MLM")
```

#### Model fit

@@

 1.	... had many benefits for me.
 2.	... has paid off for me.
 3.	... was useful for me.
 4.	... was fun.
 5.	... has brought me further regarding content.

@@

```{r}
name <- "grats_general"
model <- "
grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
"
fit <- sem(model = model, data = d, estimator = "MLM")
```

#### Model fit

@@

 13. ... to do the responsible persons a favor.
 14. ... to soothe my bad consciences.
 15. ... to fulfil my civic duty.

@@

```{r}
name <- "grats_specific"
model <- "
  grats_inf =~ GR01_01 + GR01_02 + GR01_03 
  grats_rel =~ GR01_04 + GR01_05 + GR01_06 
  grats_par =~ GR01_07 + GR01_08 + GR01_09
  grats_ide =~ GR01_10 + GR01_11 + GR01_12 
  grats_ext =~ GR01_13 + GR01_14 + GR01_15
  grats_spec =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext
"
fit <- sem(model = model, data = d, estimator = "MLM")
```

#### Model fit

@@

## Privacy Deliberation
### Items

@@

```{r}
name <- "pridel"
model <- "
pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
"
fit <- sem(model = model, data = d, estimator = "MLM")
```

#### Model fit

@@

 1. The other users seemed trustworthy.
 5. The operators of the participation platform seemed trustworthy.
 9. The website seemed trustworthy.

@@

```{r}
name <- "trust_gen"
model <- "
trust =~ TR01_01 + a*TR01_05 + a*TR01_09
"
fit <- sem(model = model, data = d, estimator = "MLM")
```

#### Model fit

@@

trust =~ trust_community + trust_provider + trust_system
"
fit <- sem(model = model, data = d, estimator = "MLM")
```

#### Model fit

@@

#### Factor loadingss

## Self-Efficacy
### Items

 1. In principle, I felt able to write a comment.
 2. I have felt technically competent enough to write a comment.
 3. Regarding content I have felt competent enough to express my opinion.
 4. I found the subject too difficult to express my opinion.
 5. I found it complicated to write a comment.
 6. I was overburdened to write a comment.

@@

```{r}
name <- "self-eff"
model <- "
self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04 + SE01_05 + SE01_06
"
fit <- sem(model = model, data = d, estimator = "MLM")
```

#### Model fit

@@

Shows significant misfit. We will run exploratory factor analyses to determine factorial structure.

### EFA

```{r}
fa.parallel(select(d, SE01_01 : SE01_06))
fa(r = select(d, SE01_01 : SE01_06), 
   nfactors = 2, fm = "ml", rotate = "promax")
```

Implies latent structure with two factors.

### CFA updated

```{r}
name <- "selfeff"
model <- "
self_eff_pos =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
self_eff_neg =~ SE01_05 + SE01_06
self_eff =~ a*self_eff_pos + a*self_eff_neg
"
fit <- sem(model = model, data = d, estimator = "MLM")
```

#### Model fit

@@

## Self-Disclosure
### Items

Let us assume that the participation platform would continue to exist in the future. Please indicate to what extent you agree with the following statements:

In the future, I am willing to ...

 1. ... discuss political issues on the participation platform.
 2. ... express my personal opinion on the participation platform.
 3. ... write comments on the participation platform.
 4. ... disclose concerns and fears on the participation platform.
 5. ... share personal experience on the participation platform.

```{r}
ggplot(gather(select(d, starts_with("WS01"))), 
       mapping = aes(x = value)) +
  geom_bar() +
  facet_wrap(~key, nrow=1) + 
  theme_bw()

des_futuse <- select(d, starts_with("WS01")) %>% 
  apply(1, mean, na.rm = TRUE) %>% 
  as.data.frame() %>% 
  summarise(m = mean(., na.rm = TRUE), sd = sd(., na.rm = TRUE))
```

```{r}
name <- "futuse"
model <- "
fut_use =~ WS01_01 + WS01_02 + WS01_03 + WS01_04 + WS01_05
"
sem(model = model, data = d)
fit <- sem(model = model, data = d, estimator = "MLM")
```

#### Model fit

#### Factor loadingss

## Baseline Model

@@

```{r}
model <- "
  pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
  grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
  grats_inf =~ GR01_01 + GR01_02 + GR01_03 
  grats_rel =~ GR01_04 + GR01_05 + GR01_06 
  grats_par =~ GR01_07 + GR01_08 + GR01_09
  grats_ide =~ GR01_10 + GR01_11 + GR01_12 
  grats_ext =~ GR01_13 + GR01_14 + GR01_15
  grats_spec =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext
  pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
  trust_gen =~ TR01_01 + TR01_05 + TR01_09
  trust_community =~ TR01_02 + TR01_03 + TR01_04
  trust_provider =~ TR01_06 + TR01_07 + TR01_08
  trust_system =~ TR01_10 + TR01_11 + TR01_12
  trust_spec =~ trust_community + trust_provider + trust_system
  self_eff_pos =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
  self_eff_neg =~ SE01_05 + SE01_06
  self_eff =~ a*self_eff_pos + a*self_eff_neg
  self_dis_lg =~ self_dis_log
"
fit_baseline <- sem(model, data = d, missing = "ML")
summary(fit_baseline, standardized = TRUE, fit.measures = TRUE)

# extract model predicted values for items & calc means
d_fs <- lavPredict(fit_baseline, type = "ov") %>% 
  as.data.frame() %>% 
  mutate(grats_gen = rowMeans(select(., starts_with("GR02")))) %>% 
  mutate(grats_spec = rowMeans(select(., starts_with("GR01")))) %>% 
  mutate(pricon = rowMeans(select(., starts_with("PC01")))) %>% 
  mutate(trust_gen = rowMeans(select(., TR01_01, TR01_05, TR01_09))) %>%
  mutate(trust_spec = rowMeans(select(., TR01_02: TR01_04, TR01_06 : TR01_12))) %>% 
  mutate(pridel = rowMeans(select(., starts_with("PD01")))) %>% 
  mutate(selfeff = rowMeans(select(., starts_with("SE01")))) %>%
  select(pricon, grats_gen, grats_spec, pridel, selfeff, trust_gen, trust_spec, self_dis_log) %>% 
  set_names(var_names_breaks) %>% 
  mutate(version = d$version)
```

@@

```{r}
# means of model predicted values
des <- rbind(des_pricon,
             des_grats_gen,
             des_grats_spec,
             des_pridel,
             des_selfeff,
             des_trust_gen,
             des_trust_spec,
             des_futuse)

factor_val_tab <- rbind(pricon_factor_val,
                        grats_general_factor_val,
                        grats_specific_factor_val,
                        pridel_factor_val,
                        selfeff_factor_val,
                        trust_gen_factor_val,
                        trust_spec_factor_val) %$%
  cbind(des[-8, ], .) %>%
  set_rownames(var_names[-8]) %T>%
  print()
# factor_val_tab %>% kable(digits = 2)
```

@@

```{r zds, fig.height=8, fig.width=8}
plot_fs_cor <- ggpairs(
  select(d_fs, -version),
  upper = list(continuous = "cor"),
  lower = list(continuous = scat_plot)) +
  theme_bw()
print(plot_fs_cor)
```

@@

# Results
## Privacy calculus
### Preregistered
#### Model "Peregistered"

We first test for multivariate normal distribution.

@@

```{r}
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 # + PC01_03 
grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
trust_community =~ TR01_02 + TR01_03 + TR01_04
trust_provider =~ TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12
trust_spec =~ trust_community + trust_provider

@@

# Covariates
self_dis_log + GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR01_02 + TR01_03 + TR01_04 + TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
"
fit_prereg <- sem(model, data = d, estimator = "MLM")
summary(fit_prereg, fit = TRUE, std = TRUE)
fit_tab(fit_prereg, scaled = TRUE)

d_coeffs_prereg <- coeffs_tab(fit_prereg, c("a1", "b1", "c1", "d1", "e1")) %>% 
  mutate(Outcome = rep("Preregistered\nmodel", 5)) %>%  
  mutate(Predictor = c("Privacy\nconcern", "Grats.\ngeneral", "Privacy\ndelib.", "Self-\nefficacy", "Trust\nspecific")) %>% 
  mutate_at(vars(Predictor), funs(factor(., c("Trust\nspecific", "Self-\nefficacy", "Privacy\ndelib.", "Grats.\ngeneral", "Privacy\nconcern"))))

plot_coeffs_prereg <- ggplot(d_coeffs_prereg, aes(x = b, y = Predictor)) + 
  theme_bw() +
  theme(axis.title.x=element_blank()) + 
  geom_vline(xintercept = 0, lwd = .75, colour = "darkgrey") + 
  geom_errorbarh(aes(xmin = ll, xmax = ul), 
                lwd = .75, colour = "grey", height = .2) +
  geom_errorbarh(aes(xmin = ll, xmax = ul),
                lwd = .75, colour = "black", height = .2) +
  geom_point(size = 2) +
  guides(color = FALSE, shape = FALSE) + 
  facet_grid(~ Outcome) +
  theme(axis.title.y = element_blank()) +
  theme(plot.title = element_text(hjust = .5)) + 
  theme(panel.spacing = unit(.9, "lines")) + 
  theme(text = element_text(size = 12))
```

### Exploratory
#### Model "adapted"

We now use specific gratifications and general trust.

```{r}
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
grats_inf =~ GR01_01 + GR01_02 + GR01_03 
grats_rel =~ GR01_04 + GR01_05 + GR01_06 
grats_par =~ GR01_07 + GR01_08 + GR01_09
grats_ide =~ GR01_10 + GR01_11 + GR01_12 
grats_ext =~ GR01_13 + GR01_14 + GR01_15
grats_spec =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext
pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
trust_gen =~ TR01_01 + TR01_05 + TR01_09

@@

# Covariates
self_dis_log + GR01_01 + GR01_02 + GR01_03 + GR01_04 + GR01_05 + GR01_06 + GR01_07 + GR01_08 + GR01_09 + GR01_10 + GR01_11 + GR01_12 + GR01_13 + GR01_14 + GR01_15 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR01_01 + TR01_05 + TR01_09 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
"
fit_adapted <- sem(model, data = d, estimator = "MLM")
summary(fit_adapted, fit = TRUE, std = TRUE)
fit_tab(fit_adapted, scaled = TRUE)

d_coeffs_adapted <- coeffs_tab(fit_adapted, c("a1", "b1", "c1", "d1", "e1")) %>% 
  mutate(Outcome = rep("Adapted\nmodel", 5)) %>%  
  mutate(Predictor = c("Privacy\nconcern", "Grats.\nspecific", "Privacy\ndelib.", "Self-\nefficacy", "Trust\ngeneral")) %>% 
  mutate_at(vars(Predictor), funs(factor(., c("Trust\ngeneral", "Self-\nefficacy", "Privacy\ndelib.", "Grats.\nspecific", "Privacy\nconcern"))))

plot_coeffs_adapted <- ggplot(d_coeffs_adapted, aes(x = b, y = Predictor)) + 
  theme_bw() +
  theme(axis.title.x=element_blank()) + 
  geom_vline(xintercept = 0, lwd = .75, colour = "darkgrey") + 
  geom_errorbarh(aes(xmin = ll, xmax = ul), 
                lwd = .75, colour = "grey", height = .2) +
  geom_errorbarh(aes(xmin = ll, xmax = ul),
                lwd = .75, colour = "black", height = .2) +
  geom_point(size = 2) +
  guides(color = FALSE, shape = FALSE) + 
  facet_grid(~ Outcome) +
  theme(axis.title.y = element_blank()) +
  theme(plot.title = element_text(hjust = .5)) + 
  theme(panel.spacing = unit(.9, "lines")) + 
  theme(text = element_text(size = 12))
```

#### Model "simple"

@@

# Covariates
self_dis_log + GR01_01 + GR01_02 + GR01_03 + GR01_04 + GR01_05 + GR01_06 + GR01_07 + GR01_08 + GR01_09 + GR01_10 + GR01_11 + GR01_12 + GR01_13 + GR01_14 + GR01_15 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 ~ male + age + edu
"
fit_simple <- sem(model, data = d, estimator = "MLM")
summary(fit_simple, fit = TRUE, std = TRUE)
fit_tab(fit_simple, scaled = TRUE)

>>>>

---
title: "How Do Like and Dislike Buttons Affect Communication?"
shorttitle : "Analyses"
output: 
  html_document:
    toc: TRUE
    toc_float:
      collapsed: FALSE
    toc_depth: 2
---

@@

```{r r-setup, include=F}
# define packages
packages <- c("cowplot", "devtools", "faoutlier", "GGally", "gganimate",
              "kableExtra", "knitr", "lavaan", "magrittr", "MVN", "psych", "pwr", 
              "quanteda", "semTools", "tidyverse")

# install packages # uncomment lines to install packages
# devtools::install_github("tdienlin/td@v.0.0.2.3")
# lapply(packages, install.packages, character.only = T, quietly = TRUE)

@@

```{r Data-Wrangling, include=F}
# load data
# please note that in a prior step several different data sets were merged using information such as case_taken or IP-addresses. To guarantee the privacy of the participants, these data were deleted after merging.
d_raw <- read_csv("data/data_raw.csv")

@@

    # recode
    edu = recode(edu_fac, 
                 "Hauptschulabschluss/Volksschulabschluss" = 1, 
                 "Noch Schüler" = 1,
                 "Realschulabschluss (Mittlere Reife)" = 1,
                 "Abschluss Polytechnische Oberschule 10. Klasse (vor 1965: 8. Klasse)" = 1,
                 "Anderer Schulabschluss:" = 1,
                 "Fachhochschulreife (Abschluss einer Fachoberschule)" = 2,
                 "Abitur, allgemeine oder fachgebundene Hochschulreife (Gymnasium bzw. EOS)" = 2,
                 "Hochschulabschluss" = 3),
    PC01_03 = 8 - PC01_03, 
    SE01_05 = 8 - SE01_05, 
    SE01_06 = 8 - SE01_06,

@@

```{r include=F}
# sample descriptives t1
n_t1 <- nrow(d)
age_t1_m <- mean(d$age, na.rm = TRUE)
male_t1_m <- mean(d$male, na.rm = TRUE)
college_t1_m <- table(d$edu)[3] / n_t1

# descriptives users
n_users <- filter(d, !is.na(post_count)) %>% nrow()

# characteristics of posts
n_comments <- sum(d$post_count, na.rm = TRUE)
n_words <- sum(d$words, na.rm = TRUE)
n_time <- sum(d$time_read_MIN, na.rm = TRUE)
n_posts <- sum(d$post_count, na.rm = TRUE)

# filter unmatched cases
d <- filter(d, !is.na(post_count) & !is.na(id_survey_t2))  # Use only completes
n_matched <- nrow(d)

# save data file with all participants to compare results
d_all <- d

# variable labels
var_names <- c("Privacy concerns", 
               "General gratifications", 
               "Specific gratifications",
               "Privacy deliberation", 
               "Self-efficacy", 
               "General trust", 
               "Specific trust",
               "Self-disclosure")

@@

# Filter Participants

```{r include=F}
# filter speeders
time_crit <- 3 # minimum time on survey
n_speeding <- nrow(filter(d, time_sum_min_t2 < time_crit))
d <- filter(d, time_sum_min_t2 >= time_crit) # Deletion of fast respondents
```

We've also inspected the data manually for cases with clear response patterns. The following cases show extreme response patterns, fast response times, and were hence removed.

```{r include=F}
# identify response patterns
resp_pattern <- c(
  "ANIEVLK9F2SW", "BN4MAOWZO7W2"  # clear response pattern
  )
n_resp_pattern <- length(resp_pattern)
# infl_cases_tokens <- infl_cases_tokens[!infl_cases_tokens %in% resp_pattern]

d %>% 
  filter(case_token %in% resp_pattern) %>% 
  select(case_token, GR01_01:SE01_06, topics_entered:reactions, -SO01_01, TIME_SUM_t1, TIME_SUM_t2) %>% 
  kable() %>% 
  kable_styling("striped") %>% 
  scroll_box(width = "100%")
d %<>% filter(!case_token %in% resp_pattern)

# sample descriptives final data set
n_final <- nrow(d)
age_final_m <- mean(d$age)
male_final_m <- mean(d$male, na.rm = TRUE)
college_final_m <- table(d$edu)[[3]] / n_final
```

# Measures
## Privacy concerns
### Items

@@

```{r}
name <- "pricon"
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_03 + PC01_04 + PC01_05 + PC01_06 + PC01_07
"
fit <- sem(model = model, data = d, estimator = "MLR", missing = "ML")
```

Model fit:

@@

Factor loadings:

@@

### CFA 2

```{r}
name <- "pricon"
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
"
fit <- sem(model = model, data = d, estimator = "MLR", missing = "ML")
```

Model fit:

@@

 1.	... had many benefits for me.
 2.	... has paid off for me.
 3.	... was worthwhile.
 4.	... was fun.
 5.	... has brought me further regarding content.

@@

```{r}
name <- "grats_general"
model <- "
grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
"
fit <- sem(model = model, data = d, estimator = "MLR", missing = "ML")
```

Model fit:

@@

 13. ... to do the responsible persons a favor.
 14. ... to soothe my guilty consciences.
 15. ... to fulfil my civic duty.

@@

```{r}
name <- "grats_specific"
model <- "
  grats_inf =~ GR01_01 + GR01_02 + GR01_03 
  grats_rel =~ GR01_04 + GR01_05 + GR01_06 
  grats_par =~ GR01_07 + GR01_08 + GR01_09
  grats_ide =~ GR01_10 + GR01_11 + GR01_12 
  grats_ext =~ GR01_13 + GR01_14 + GR01_15
  grats_spec =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext
"
fit <- sem(model = model, data = d, estimator = "MLR", missing = "ML")
```

Model fit:

@@

## Privacy deliberation
### Items

@@

```{r}
name <- "pridel"
model <- "
pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
"
fit <- sem(model = model, data = d, estimator = "MLR", missing = "ML")
```

Model fit:

@@

&nbsp;&nbsp;&nbsp;1. The other users seemed trustworthy.  
&nbsp;&nbsp;&nbsp;5. The operators of the participation platform seemed trustworthy.  
&nbsp;&nbsp;&nbsp;9. The website seemed trustworthy.

@@

```{r}
name <- "trust_gen"
model <- "
trust =~ TR01_01 + a*TR01_05 + a*TR01_09
"
fit <- sem(model = model, data = d, estimator = "MLR", missing = "ML")
```

Model fit:

@@

trust =~ trust_community + trust_provider + trust_system
"
fit <- sem(model = model, data = d, estimator = "MLR", missing = "ML")
```

Model fit:

```{r warning=T}
(factor_val <- fit_tab(fit, reliability = TRUE, scaled = TRUE))
assign(paste0(name, "_factor_val"), factor_val)
```

Factor loadings:

### CFA 2

Because there was Heywoodcase, we now also run a model in which the subdimensions `provider` and `system` are combined.

```{r}
name <- "trust_spec"
model <- "
trust_community =~ TR01_02 + TR01_03 + TR01_04
trust_provider =~ TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12
trust =~ b*trust_community + b*trust_provider
"
fit <- sem(model = model, data = d, estimator = "MLR", missing = "ML")
```

Model fit:

@@

Factor loadings:

```{r}
inspect(fit,what="std")$lambda
```
Warning disappears, results show adequate fit.

## Self-efficacy
### Items

 1. In principle, I felt able to write a comment.
 2. I felt technically competent enough to write a comment.
 3. In terms of the topic, I felt competent enough to express my opinion.
 4. I found it easy to express my opinion regarding the topic.
 5. I found it complicated to write a comment.
 6. I was overburdened to write a comment.

@@

```{r}
name <- "self-eff"
model <- "
self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04 + SE01_05 + SE01_06
"
fit <- sem(model = model, data = d, estimator = "MLR", missing = "ML")
```

Model fit:

@@

Shows significant misfit. We will delete inverted items, while allowing covariations between Items 1 and 2 (tech-oriented) and Items 3 and 4 (topic-oriented).

### CFA 2

```{r}
name <- "selfeff"
model <- "
self_eff_pos =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
SE01_01 ~~ x*SE01_02
SE01_03 ~~ x*SE01_04
"
fit <- sem(model = model, data = d, estimator = "MLR", missing = "ML")
```

Model fit:

@@

## Baseline model

@@

```{r}
model_baseline <- "
  pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
  grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
  grats_inf =~ GR01_01 + GR01_02 + GR01_03 
  grats_rel =~ GR01_04 + GR01_05 + GR01_06 
  grats_par =~ GR01_07 + GR01_08 + GR01_09
  grats_ide =~ GR01_10 + GR01_11 + GR01_12 
  grats_ext =~ GR01_13 + GR01_14 + GR01_15
  grats_spec =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext
  pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
  trust_gen =~ TR01_01 + TR01_05 + TR01_09
  trust_community =~ TR01_02 + TR01_03 + TR01_04
  trust_provider =~ TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12
  trust_spec =~ trust_community + trust_provider
  self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
    SE01_01 ~~ x*SE01_02
    SE01_03 ~~ x*SE01_04
  self_dis_lg =~ self_dis_log

  self_dis_lg ~~ a1*pri_con + b1*grats_gen + c1*pri_delib + d1*self_eff + e1*trust_spec + f1*trust_gen + g1*grats_spec
"
fit_baseline <- sem(model_baseline, data = d, missing = "ML")
summary(fit_baseline, standardized = TRUE, fit.measures = TRUE)
```

@@

```{r}
# extract model predicted values for items & calc means
d_fs <- lavPredict(fit_baseline, type = "ov") %>% 
  as.data.frame() %>% 
  mutate(version = d$version, 
         grats_gen_fs = rowMeans(select(., starts_with("GR02"))),
         grats_spec_fs = rowMeans(select(., starts_with("GR01"))), 
         pri_con_fs = rowMeans(select(., starts_with("PC01"))),
         trust_gen_fs = rowMeans(select(., TR01_01, TR01_05, TR01_09)),
         trust_spec_fs = rowMeans(select(., TR01_02: TR01_04, TR01_06 : TR01_12)),
         pri_del_fs = rowMeans(select(., starts_with("PD01"))),
         self_eff_fs = rowMeans(select(., starts_with("SE01")))) %>%
  select(version, pri_con_fs, grats_gen_fs, grats_spec_fs, pri_del_fs, self_eff_fs, trust_gen_fs, trust_spec_fs, self_dis_log)

# combine d with d factor scores
d %<>% cbind(select(d_fs, -version, -self_dis_log))

# rename for plotting
d_fs %<>% set_names(c("version", var_names_breaks))

# means of model predicted values
des <- rbind(des_pricon,
             des_grats_gen,
             des_grats_spec,
             des_pridel,
             des_selfeff,
             des_trust_gen,
             des_trust_spec)

factor_val_tab <- rbind(pricon_factor_val,
                        grats_general_factor_val,
                        grats_specific_factor_val,
                        pridel_factor_val,
                        selfeff_factor_val,
                        trust_gen_factor_val,
                        trust_spec_factor_val) %$%
  cbind(des[-8, ], .) %>%
  set_rownames(var_names[-8]) %T>%
  print()
```

@@

```{r zds, fig.height=8, fig.width=8}
fig_fs_cor <- ggpairs(
  select(d_fs, -version),
  upper = list(continuous = "cor"),
  lower = list(continuous = wrap(td::scat_plot, coords = c(1, 7, 0, 7)))) +
  theme_bw()
print(fig_fs_cor)
```

@@

# Assumptions
## Multivariate normal distribution

@@

## Influential cases

In what follows we test for influential cases in baseline model, to detect potentially corrupt data (e.g., people who provided response patterns). Specifically, we compute Cook's distance.

```{r}
cooks_dis <- gCD(d, model_baseline)
plot(cooks_dis)
```

The following ten cases have a particularly strong influence on the baseline model.

```{r}
infl_cases <- invisible(rownames(print(cooks_dis)))
```

Let's inspect these cases.

```{r}
infl_cases_tokens <- d[infl_cases, "case_token"] %>% as_vector()
d %>% 
  filter(case_token %in% infl_cases_tokens) %>% 
  select(case_token, GR01_01:SE01_06, topics_entered:reactions, -SO01_01, TIME_SUM_t1, TIME_SUM_t2) %>% 
  kable() %>% 
  kable_styling("striped") %>% 
  scroll_box(width = "100%")
```

These data do not reveal potential cases of response patterns. Indeed, answer times suggest that respondents were diligent.

# Results
## Privacy calculus
### Model "Peregistered"

```{r}
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 
grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
  SE01_01 ~~ x*SE01_02
  SE01_03 ~~ x*SE01_04
trust_community =~ TR01_02 + TR01_03 + TR01_04
trust_provider =~ TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12
trust_spec =~ trust_community + trust_provider

@@

# Covariates
self_dis_log + GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR01_02 + TR01_03 + TR01_04 + TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
"
fit_prereg <- sem(model, data = d, estimator = "MLR", missing = "ML")
summary(fit_prereg, fit = TRUE, std = TRUE)
rsquare_fit_prereg <- inspect(fit_prereg, what = "rsquare")["self_dis_log"]
```

### Model "Adapted"

Building on the preregistered model, instead of general gratifications and specific trust, we now use specific gratifications and general trust.

```{r}
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
grats_inf =~ GR01_01 + GR01_02 + GR01_03 
grats_rel =~ GR01_04 + GR01_05 + GR01_06 
grats_par =~ GR01_07 + GR01_08 + GR01_09
grats_ide =~ GR01_10 + GR01_11 + GR01_12 
grats_ext =~ GR01_13 + GR01_14 + GR01_15
grats_spec =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext
pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
  SE01_01 ~~ x*SE01_02
  SE01_03 ~~ x*SE01_04
trust_gen =~ TR01_01 + TR01_05 + TR01_09

@@

# Covariates
self_dis_log + GR01_01 + GR01_02 + GR01_03 + GR01_04 + GR01_05 + GR01_06 + GR01_07 + GR01_08 + GR01_09 + GR01_10 + GR01_11 + GR01_12 + GR01_13 + GR01_14 + GR01_15 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR01_01 + TR01_05 + TR01_09 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
"
fit_adapted <- sem(model, data = d, estimator = "MLR", missing = "ML", missing = "ML")
summary(fit_adapted, fit = TRUE, std = TRUE)
```

### Model "Simple"

@@

# Covariates
self_dis_log + GR01_01 + GR01_02 + GR01_03 + GR01_04 + GR01_05 + GR01_06 + GR01_07 + GR01_08 + GR01_09 + GR01_10 + GR01_11 + GR01_12 + GR01_13 + GR01_14 + GR01_15 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 ~ male + age + edu
"
fit_simple <- sem(model, data = d, estimator = "MLR", missing = "ML")
summary(fit_simple, fit = TRUE, std = TRUE)
rsquare_fit_simple <- inspect(fit_simple, what = "rsquare")["self_dis_log"]
```

### Comparison
